DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2018-01-24 paper/cvpr2018/cvpr2018_3790.tex
Paper writing, result plot figure resize

\subsection{Sequence modeling}

@@

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$. The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embeddings with higher level semantic information. Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.[????]. The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.

@@

%\setlength{\fboxsep}{1pt}%
%\setlength{\fboxrule}{1pt}%
\begin{figure*}[t]
       \centering
        \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4cm,height=3cm, clip]{figures/precision_plot_2d.png}
    \caption{\small{2D Precision plot}}
        \end{subfigure}
        \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4cm,height=3cm, clip]{figures/success_plot_2d.png}
        \caption{\small{2D success plot}}
        \end{subfigure}
       \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4cm,height=3cm, clip]{figures/precision_plot_3d_20cm.png}
    \caption{\small{3D precision plot}}
        \end{subfigure}
               \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4cm,height=3cm, clip]{figures/success_plot_3d.png}
        \caption{\small{3D Success plot}}
        \end{subfigure}

>>>>

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
        \caption{
        \small{TODO: SEGLSTM HERE!}
        }
        \label{fig:SEGLSTM}
\end{figure}
\subsection{Sequence modeling}

@@

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$. The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embeddings with higher level semantic information. Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}. The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.

@@

%\setlength{\fboxsep}{1pt}%
%\setlength{\fboxrule}{1pt}%
\begin{figure*}[t]
       \centering
        \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/precision_plot_2d.png}
    \caption{\small{2D Precision plot}}
        \end{subfigure}
        \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/success_plot_2d.png}
        \caption{\small{2D success plot}}
        \end{subfigure}
       \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/precision_plot_3d_20cm.png}
    \caption{\small{3D precision plot}}
        \end{subfigure}
               \begin{subfigure}[c]{0.24\textwidth}
        \centering
                \includegraphics[width=4.2cm,height=3.5cm, clip]{figures/success_plot_3d.png}
        \caption{\small{3D Success plot}}
        \end{subfigure}
